### 2021-08-10 paper/paper.tex
Remove color boxes around links
Shorten list of goals
Various fixes here and there

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

@@

We are broadly interested in simulation-focused scientific computing, in particular
numerical approximations for hyperbolic partial differential equations (PDEs), computational fluid dynamics (CFD),
and related problems. The focus of our research ranges from specific applications
in CFD to general multi-physics coupling strategies to the development and analysis of high-order numerical methods
our simulations are built upon. In addition, we are academics and involved in teaching
students in these areas of science. Thus, we would like to have a
code that is
\begin{enumerate}
  \item extendable to be useful for research and development
  \item easy to apply/understand to be useful for students/collaborators
  \item fast enough to be useful beyond small toy problems
\end{enumerate}
Additionally, we are greedy\footnote{See \url{https://julialang.org/blog/2012/02/why-we-created-julia/}}
and wish to include all these features within a single code.
Roughly one year of collaborative work has resulted in the current version of
\trixi\footnote{\url{https://github.com/trixi-framework/Trixi.jl}}, providing adaptive
high-order numerical simulations of hyperbolic PDEs
in Julia \cite{bezanson2017julia}. Starting as an experiment, we have been able
to reach more and more of our goals with \trixi.

@@

\trixi is designed as a library of high-order methods for hyperbolic PDEs of
the form
\begin{equation}
\label{eq:hcl}
  \partial_t u(t, x) + \sum_{j=1}^d \partial_{x_j} f^j(u) = s(t, x, u),
  \quad t \in (0, T), x \in \Omega,
\end{equation}
in $d \in \{1, 2, 3\}$ space dimensions. Here, the independent variables are
time $t$ and space coordinates $x \in \Omega \subset \mathbb{R}^d$. The conserved
quantities are denoted as $u$, \eg, mass, momentum, and energy for the compressible
Euler equations of an ideal gas.
The physical model is specified by the fluxes $f^j$ and the source term $s$.
In addition, suitable initial and boundary conditions (ICs, BCs) are required.
\trixi also handles non-conservative PDE terms as in the shallow water equations or magnetohydrodynamics equations
with divergence cleaning.

@@

As of version v0.3.55 (August 2021), \trixi concentrates mainly on discontinuous
Galerkin (DG) methods \cite{hesthaven2007nodal, kopriva2009implementing}.
In particular, it has a focus on entropy-conservative and -dissipative methods
\cite{tadmor1987numerical, lefloch2002fully, fisher2013discretely,
ranocha2018comparison, chen2017entropy}. Currently, \trixi comes with the
following features.
\begin{itemize}
  \item 1D, 2D, and 3D simulations on line/quad/hex/simplex meshes
  \begin{itemize}
    \item Cartesian and curvilinear meshes
    \item Conforming and non-conforming meshes
    \item Structured and unstructured meshes
    \item Hierarchical quadtree/octree grid with adaptive refinement
    \item Forests of quadtrees/octrees with \texttt{p4est} \cite{burstedde2011p4est}
          via P4est.jl\footnote{\url{https://github.com/trixi-framework/P4est.jl}}
  \end{itemize}

@@

Figure~\ref{fig:kelvin_helmholtzs} demonstrates demonstrates nonlinear stability
obtained with entropy-stable methods and adaptive mesh refinement applied to a
classical Kelvin-Helmholtz flow instability problem.
\begin{figure}[!h]
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_density_t2}
    \caption{Density at time $t = 2$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_mesh_t2}
    \caption{Mesh at time $t = 2$.}
  \end{subfigure}%
  \\
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_density_t3}
    \caption{Density at time $t = 3$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_mesh_t3}
    \caption{Mesh at time $t = 3$.}
  \end{subfigure}%
  \caption{Numerical solutions of a Kelvin-Helmholtz instability using
           entropy-stable methods and adaptive mesh refinement for the
           compressible Euler equations.}
  \label{fig:kelvin_helmholtzs}
\end{figure}

Figure~\ref{fig:pressure_waves} shows the approximation
of acoustic perturbation equations~\cite{ewert2003acoustic} wave scattering on a
curvilinear and unstructured domain. The 2D quadrilateral mesh in
Figure~\ref{fig:ginger_mesh} was generated with
HOHQMesh.jl\xspace\footnote{\url{https://github.com/trixi-framework/HOHQMesh.jl}}.
\begin{figure}[!h]
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_00}
    \caption{Pressure at time $t = 0$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_08}
    \caption{Pressure at time $t = 8$.}
  \end{subfigure}%
  \\
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_16}
    \caption{Pressure at time $t = 16$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_mesh}
    \caption{Unstructured quad mesh.}
    \label{fig:ginger_mesh}
  \end{subfigure}%
  \caption{Numerical solutions of pressure wave scattering for the acoustic
                perturbation equations at three times as well as the unstructured,
                curvilinear quadrilateral mesh.}
  \label{fig:pressure_waves}
\end{figure}

>>>>

% JuliaCon proceedings template
% \documentclass{juliacon}
% FIXME sloede: I personally hate these color boxes around links, but maybe we should not mess with
% the official style?
\documentclass[hidelinks]{juliacon}
\setcounter{page}{1}

@@

We are broadly interested in simulation-focused scientific computing, in particular
numerical approximations for hyperbolic partial differential equations (PDEs), computational fluid dynamics (CFD),
and related problems. The focus of our research ranges from specific applications
in CFD to general multi-physics coupling strategies to the development and analysis of high-order numerical methods
our simulations are built upon. In addition, we are academics and involved in teaching
students in these areas of science. Thus, we would like to have a
code that is
\begin{enumerate}
  \item extendable for research and development,
  \item easy to apply/understand for students/collaborators,
  \item fast enough for applied 3D problems.
\end{enumerate}
Additionally, we are greedy\footnote{See \url{https://julialang.org/blog/2012/02/why-we-created-julia/}}
and wish to include all these features within a single code.
Roughly one year of collaborative work has resulted in the current version of
\trixi\footnote{\url{https://github.com/trixi-framework/Trixi.jl}}, providing adaptive
high-order numerical simulations of hyperbolic PDEs
in Julia \cite{bezanson2017julia}. Starting as an experiment, we have been able
to reach more and more of our goals with \trixi.

@@

\trixi is designed as a library of high-order methods for hyperbolic PDEs of
the form
\begin{equation}
\label{eq:hcl}
  \partial_t u(t, x) + \sum_{j=1}^d \partial_{x_j} f^j(u) = s(t, x, u),
  \quad t \in (0, T), x \in \Omega,
\end{equation}
in $d \in \{1, 2, 3\}$ space dimensions. Here, the independent variables are
time $t$ and space coordinates $x \in \Omega \subset \mathbb{R}^d$. The conserved
quantities are denoted as $u$, \eg, mass, momentum, and energy for the compressible
Euler equations of an ideal gas.
The physical system is specified by the fluxes $f^j$ and the source term $s$.
In addition, suitable initial and boundary conditions (ICs, BCs) are required.
\trixi also handles non-conservative PDE terms as in the shallow water equations or magnetohydrodynamics equations
with divergence cleaning.

@@

As of version v0.3.55 (August 2021), \trixi concentrates mainly on discontinuous
Galerkin (DG) methods \cite{hesthaven2007nodal, kopriva2009implementing}.
In particular, it has a focus on entropy-conservative and -dissipative methods
\cite{tadmor1987numerical, lefloch2002fully, fisher2013discretely,
ranocha2018comparison, chen2017entropy}. Currently, \trixi offers the
following features:
\begin{itemize}
  \item 1D, 2D, and 3D simulations on line/quad/hex/simplex meshes
  \begin{itemize}
    \item Cartesian and curvilinear meshes
    \item Conforming and non-conforming meshes
    \item Structured and unstructured meshes
    \item Hierarchical quadtree/octree grid with adaptive refinement
    \item Forests of quadtrees/octrees with \texttt{p4est} \cite{burstedde2011p4est}
          via P4est.jl\footnote{\url{https://github.com/trixi-framework/P4est.jl}}
  \end{itemize}

@@

Figure~\ref{fig:kelvin_helmholtzs} demonstrates nonlinear stability
obtained with entropy-stable methods and adaptive mesh refinement applied to a
classical Kelvin-Helmholtz flow instability problem.
\begin{figure}[!h]
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_density_t2}
    \caption{Density at time $t = 2$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_mesh_t2}
    \caption{Mesh at time $t = 2$.}
  \end{subfigure}%
  \\
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_density_t3}
    \caption{Density at time $t = 3$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/kelvin_helmholtz_mesh_t3}
    \caption{Mesh at time $t = 3$.}
  \end{subfigure}%
  \caption{Numerical solutions of a Kelvin-Helmholtz instability using
           entropy-stable methods and adaptive mesh refinement for the
           compressible Euler equations.}
  \label{fig:kelvin_helmholtzs}
\end{figure}

Figure~\ref{fig:pressure_waves} shows the approximation
of acoustic perturbation equations~\cite{ewert2003acoustic} wave scattering on a
curvilinear and unstructured domain. The 2D quadrilateral mesh used in the simulation
(Figure~\ref{fig:ginger_mesh}) was generated with
HOHQMesh.jl\xspace\footnote{\url{https://github.com/trixi-framework/HOHQMesh.jl}}.
\begin{figure}[!h]
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_00}
    \caption{Pressure at time $t = 0$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_08}
    \caption{Pressure at time $t = 8$.}
  \end{subfigure}%
  \\
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_16}
    \caption{Pressure at time $t = 16$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_mesh}
    \caption{Unstructured quad mesh.}
    \label{fig:ginger_mesh}
  \end{subfigure}%
  \caption{Numerical solutions of pressure wave scattering for the acoustic
                perturbation equations at three points in time as well as the unstructured,
                curvilinear quadrilateral mesh.}
  \label{fig:pressure_waves}
\end{figure}
